---
title: "Weekly Report of Peak Shaving for Fort William TS Power Station"
output:
  bookdown::html_document2
params:
  report_start: '2018-04-07'
header-includes:
 \usepackage{float}
---
<style type="text/css">
  body{
  font-size: 12pt;
  }
</style>
---
date: from `r as.Date(params$report_start)-6` to `r params$report_start` 
---

```{r echo=FALSE,warning=FALSE,message=FALSE, results='hide', out.width='100%'}
require("keras")
require("jsonlite")
require("lubridate")
require("htmlwidgets")
require("plotly")
require("RMySQL")
require("RODBC")
require("tidyverse")
require("DMwR")
require("zoo")
require("ggplot2")
require("mailR")
require("recipes")
require("dplyr")
library(lubridate)
library(Cubist)
library(caTools)
library(rpart)
library (dplyr)
library(caret)
library(rpart.plot)
library(reticulate)
library(readr)
library(plotly)
library(stringr)
library(keras)
library(recipes)
library(xgboost)
library(h2o)
library(hrbrthemes)
library(chron)
library(Metrics)
library(scales)
library(zoo)
library('dplyr')
if(!require(philentropy)){
  install.packages("philentropy")
  library(philentropy)
}
if(!require(webshot)){
  install.packages("webshot")
  webshot::install_phantomjs()
  library(webshot)
}
h2o.init(nthreads=-1, max_mem_size="2G")
setwd("D:/Hydro-prediction-System/ui")


data <- read.csv("total_dataset.csv", header=TRUE, sep=",", na.strings=c("NA", "NULL"),stringsAsFactors=FALSE)
scale_data<-scale(data$fwts)
data$fwts<-scale(data$fwts)
source('Make_prediction.R')
source('weekly.R')
source("plot_function.R")
battery_size<-4000
l_of_p<-make_prediction_weekly(params$report_start)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period
success<-!l_of_p$hours[which.max(monthreport_shaved)]==l_of_p$xcoord_list$test
  #l_of_p$hours[which.max(monthreport_shaved)]==l_of_p$xcoord_list$test
```


# Overview
This weekly report analyzes the Peak Shaving system of Fort William TS power station from <span style='color:red'>`r as.Date(params$report_start)-6`</span> to <span style='color:red'>`r as.Date(params$report_start)`</span>. This report contains four sections: First, the graphical results of peak shaving activities of power consumption. Second, the numerical results peak shaving activities of power consumption and expected bill saving. Third, the weekly performance of energy forecasting models. Four, detailed peak shaving activities of the highest five peak days during this month. 

# Monthly Peaking Shaving Results
Figure \@ref(fig:fig1) shows a weekly forecasting graph. The black line describes the actual power consumption curve; the red line describes the prediction curve and the yellow line describes the battery discharging period set by the predicted peak.
<br><br>

```{r fig1,fig.cap = "weekly forecasting graph\\label{fig1}",echo=FALSE,message=FALSE, out.width='100%'}
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>


Figure (\@ref(fig:fig2)) shows a comparison of the expected power consumption curve(black) and after the peak-shaving curve(red). According to figure (\@ref(fig:fig2)), `r if(success){sprintf("The highest peak of power consumption of the month is reduced from <span style='color:red'>%s</span>kW (<span style='color:blue'>%s</span>) to <span style='color:red'> %s</span>kW (<span style='color:blue'> %s</span>).",format(l_of_p$ymax_list$test, scientific=FALSE),l_of_p$xcoord_list$test,format(max(monthreport_shaved),scientific=FALSE),l_of_p$hours[which.max(monthreport_shaved)])}else{sprintf("The highest peak of power consumption of the month remains <span style='color:red'>%s</span>kW (<span style='color:blue'>%s</span>).",format(l_of_p$ymax_list$test, scientific=FALSE),l_of_p$xcoord_list$test)}` Figure (\@ref(fig:fig3)) shows the detailed peak shaving result of the highest peak of the month which is in <span style='color:blue'>as.Date(l_of_p$xcoord_list$test)</span>.

<br><br>

```{r fig2,fig.cap = "weekly Peak Shaving Activies graph\\label{fig2}",echo=FALSE, out.width='100%'}
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ monthreport_shaved,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Shaved Data",
    line = list(color = 'red')
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Actual Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Acutal Peak point", l_of_p$ymax_list$test),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  ) %>%
  add_trace(
    x =  ~ l_of_p$hours[which.max(monthreport_shaved)],
    y =  ~ max(monthreport_shaved),
    mode = 'markers',
    type = 'scatter',
    name = paste("Shaved Peak point", max(monthreport_shaved)),
    marker = list(color = ("red"),size=13,symbol="triangle-up")
  ) %>%
  layout(
    title = paste('Expected consumption and After-Shaved consumption'),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```

<br><br>


```{r fig3,fig.cap = "Highest peak day\\label{fig3}",echo=FALSE, out.width='100%'}
highest<-l_of_p$hours[l_of_p$test==l_of_p$ymax_list]

dayreport<-make_prediction_testing(as.Date(highest))
#dayreport
#daily_plot_simple(dayreport)

gap<-30
low_peak <-
  dayreport$hours[which.min(dayreport$AVG)]


charging_range <- interval(dayreport$xcoord_list$mean_s-gap*60, dayreport$xcoord_list$mean_s+gap*60)
peak_period<-ifelse(dayreport$hours %within% charging_range , dayreport$AVG, NA)
charging_range <- interval(dayreport$xcoord_list$mean_s-gap*60+300, dayreport$xcoord_list$mean_s+gap*60-300)
#make range smaller to remove the gap between normal period and peak period

discharging_range <- interval(low_peak-gap*60, low_peak+gap*60)
low_peak_period<-ifelse(dayreport$hours %within% discharging_range , dayreport$AVG, NA)
discharging_range <- interval(low_peak-gap*60+300, low_peak+gap*60-300)


dayreport_shaved<-ifelse(dayreport$hours %within% charging_range,dayreport$test-battery_size,dayreport$test)

plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ dayreport_shaved,
    x =  ~ dayreport$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Shaved Data",
    line = list(color = 'red')
  ) %>%
  add_trace(
    y =  ~ dayreport$test,
    x =  ~ dayreport$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Actual Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    x =  ~ dayreport$xcoord_list$test,
    y =  ~ dayreport$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Actual Peak point", dayreport$ymax_list$test),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  ) %>%
  add_trace(
    x =  ~ dayreport$hours[which.max(dayreport_shaved)],
    y =  ~ max(dayreport_shaved),
    mode = 'markers',
    type = 'scatter',
    name = paste("Shaved Peak point", max(dayreport_shaved)),
    marker = list(color = ("red"),size=13,symbol="triangle-up")
  ) %>%
  layout(
    title = paste(strftime(as.POSIXct(dayreport$hours[100]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )

```


<br><br>

# The Peak Shaving and Cost Reduction




As shown in Table(\@ref(tab:table0)), `r if(success){sprintf("the expected peak of power consumption is <span style='color:red'>%s</span>kW occur at <span style='color:blue'>%s</span>. After the peak-shaving activities, the highest peak of this month reduces to <span style='color:red'> %s</span>kW at <span style='color:blue'> %s</span>. The weekly energy purchasing cost reduces from $<span style='color:red'>%s</span> to $<span style='color:red'>%s</span>, which saves $<span style='color:red'>%s</span>.",format(l_of_p$ymax_list$test, scientific=FALSE),l_of_p$xcoord_list$test,format(max(monthreport_shaved),scientific=FALSE),l_of_p$hours[which.max(monthreport_shaved)],format(l_of_p$ymax_list$test/2, scientific=FALSE),format(max(monthreport_shaved)/2, scientific=FALSE),format((l_of_p$ymax_list$test-max(monthreport_shaved))/2, scientific=FALSE))}else{sprintf("The peak of power consumption remains <span style='color:red'>%s</span>kW occur at <span style='color:blue'>%s</span>. After the peak-shaving activities, the highest peak is not been reduced. The weekly energy purchasing cost is $<span style='color:red'>%s</span>. The detailed situation is in Section 2: The results of Peak Shaving.",format(l_of_p$ymax_list$test),l_of_p$xcoord_list$test,format(l_of_p$ymax_list$test/2, scientific=FALSE))}`

<br><br>

```{r table0,table.cap = "weekly Results Table\\label{table0}",echo=FALSE, out.width='100%',fig.pos="H"}

weekly_table<-as.data.frame(c("Power Consumption(kW)", "Billing($)"))
weekly_table$Expected_Peak_of_the_Month<-c(format(l_of_p$ymax_list$test, scientific=FALSE),format(l_of_p$ymax_list$test/2, scientific=FALSE))
weekly_table$Shaved_Peak_of_the_Month<-c(format(max(monthreport_shaved),scientific=FALSE),format(max(monthreport_shaved)/2,scientific=FALSE))
weekly_table$Total_Reduction<-c(l_of_p$ymax_list$test-max(monthreport_shaved),(l_of_p$ymax_list$test-max(monthreport_shaved))/2)
colnames(weekly_table)<-c('Parameter','Weekly Expected Peak', 
                           'Weekly Shaved Peak',"Total Reduction")
knitr::kable(weekly_table,digits = 2,caption = "weekly Results Table")
```

<br><br>
# System Performance
In this energy forecasting system, we combine four different models. Table (\@ref(tab:table1)) show the weekly performance of each model. There are four machine learning algorithms in total: Cubist, Xgboost, (feedforward) Neural Network and LSTM (Long short-term memory). The ensemble model combines all four algorithms and battery discharging events base on the ensemble model. 

<br><br>

```{r table1,table.cap = "weekly Models Performance\\label{table1}",echo=FALSE, out.width='100%'}
date<-as.Date(params$report_start)-6

list_of_prediction<-make_prediction_testing(date)
result_list<-list_of_prediction$results

for (i in 1:6){#set up the training end

  list_of_prediction<-make_prediction_testing(date+i)
  result_list<-rbind(result_list,list_of_prediction$results)
  date<-date+1  
}

#parameter, Cubist , Xgboost, Random Forest, Nerual Network, Ensemble System



result_table<-as.data.frame(c("rRMSE","Average Peak time error", "percentage of daily peak shaved"))
result_table$Cubist<-c(mean(result_list$RMSE_cubist),mean(abs(result_list$Peak_dif_cubist)),mean(abs(result_list$Peak_dif_cubist)<30))
result_table$xgboost<-c(mean(result_list$RMSE_xgboost),mean(abs(result_list$Peak_dif_xgboost)),mean(abs(result_list$Peak_dif_xgboost)<30))
result_table$RF<-c(mean(result_list$RMSE_RF),mean(abs(result_list$Peak_dif_RF)),mean(abs(result_list$Peak_dif_RF)<30))
result_table$NN<-c(mean(result_list$RMSE_NN),mean(abs(result_list$Peak_dif_NN)),mean(abs(result_list$Peak_dif_NN)<30))
result_table$LSTM<-c(mean(result_list$RMSE_LSTM),mean(abs(result_list$Peak_dif_LSTM)),mean(abs(result_list$Peak_dif_LSTM)<30))
result_table$AVG<-c(mean(result_list$RMSE_AVG),mean(abs(result_list$Peak_dif_mean_s)),mean(abs(result_list$Peak_dif_mean_s)<30))
colnames(result_table)<-c('Parameter', 'Cubist' , 'Xgboost', 'Random Forest', 'Nerual Network',"LSTM", 'Ensemble System')
knitr::kable(result_table,digits = 2,caption = " Models Performance")

```
<br><br>



The accuracy of energy forecasting on the highest peak of the month is an important factor to measure the performance of each model. Figure (\@ref(fig:fig4)) show the performance of each model on the day with highest peak.


<br><br>
```{r fig4,fig.cap = "Daily Models Performance\\label{fig4}",echo=FALSE, out.width='100%'}
daily_plot(dayreport)
```