---
title: "Yearly Report of Peak Shaving for Fort William TS Power Station"
output:
  bookdown::html_document2:
    toc: true
params:
  report_month: '2018-04-01'
---
<style type="text/css">
  body{
  font-size: 12pt;
  }
</style>
---
date: `r format(as.Date(params$report_month), "%Y")`
---

```{r echo=FALSE,warning=FALSE,message=FALSE, results='hide', out.width='100%'}
require("keras")
require("jsonlite")
require("lubridate")
require("htmlwidgets")
require("plotly")
require("RMySQL")
require("RODBC")
require("tidyverse")
require("DMwR")
require("zoo")
require("ggplot2")
require("mailR")
require("recipes")
require("dplyr")
library(htmlwidgets)
library(lubridate)
library(Cubist)
library(caTools)
library(rpart)
library (dplyr)
library(caret)
library(rpart.plot)
library(reticulate)
library(readr)
library(plotly)
library(stringr)
library(keras)
library(recipes)
library(xgboost)
library(h2o)
library(hrbrthemes)
library(chron)
library(Metrics)
library(scales)
library(zoo)
library('dplyr')
if(!require(kableExtra)){
  install.packages("kableExtra")
  library(kableExtra)
}
if(!require(philentropy)){
  install.packages("philentropy")
  library(philentropy)
}
if(!require(webshot)){
  install.packages("webshot")
  webshot::install_phantomjs()
  library(webshot)
}
h2o.init(nthreads=-1, max_mem_size="2G")
setwd("D:/Hydro-prediction-System/ui")


data <- read.csv("total_dataset.csv", header=TRUE, sep=",", na.strings=c("NA", "NULL"),stringsAsFactors=FALSE)
scale_data<-scale(data$fwts)
data$fwts<-scale(data$fwts)
source('Make_prediction.R')
source('Monthly.R')
source("plot_function.R")
battery_size<-4000
l_of_p<-make_prediction_monthly(params$report_month)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period
success<-!l_of_p$hours[which.max(monthreport_shaved)]==l_of_p$xcoord_list$test
  #l_of_p$hours[which.max(monthreport_shaved)]==l_of_p$xcoord_list$test
E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
yearly_table<-data.frame("January",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(yearly_table)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")

```


# Overview
This yearly report analyzes the Peak Shaving system of Fort William TS power station during <span style='color:red'>`r format(as.Date(params$report_month), "%Y")`</span>. This report contains two main sections: First, the graphical results of each month of this year, from January to December respectively. Each figure represents a monthly forecasting graph of the month. The black line describes the actual power consumption curve; the red line describes the prediction curve and the yellow line describes the battery discharging period set by the predicted peak. Second, a table of monthly numerical results peak shaving activities of power consumption and expected bill saving.

# January 

<br><br>
```{r fig0,fig.cap = "Monthly forecasting graph\\label{fig0}",echo=FALSE,message=FALSE, out.width='100%'}
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# February  

<br><br>
```{r fig1,fig.cap = "Monthly forecasting graph\\label{fig1}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(1)
#l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period


E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("February",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# March  

<br><br>
```{r fig2,fig.cap = "Monthly forecasting graph\\label{fig2}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(2)
#l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("March",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# April  

<br><br>
```{r fig3,fig.cap = "Monthly forecasting graph\\label{fig3}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(3)
#l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("April",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# May  

<br><br>
```{r fig4,fig.cap = "Monthly forecasting graph\\label{fig4}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(1)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("May",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# June  

<br><br>
```{r fig5,fig.cap = "Monthly forecasting graph\\label{fig5}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(2)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("June",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# July  

<br><br>
```{r fig6,fig.cap = "Monthly forecasting graph\\label{fig6}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(3)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("July",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# August  

<br><br>
```{r fig7,fig.cap = "Monthly forecasting graph\\label{fig7}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(4)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("August",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# September  

<br><br>
```{r fig8,fig.cap = "Monthly forecasting graph\\label{fig8}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(5)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("September",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# October 

<br><br>
```{r fig9,fig.cap = "Monthly forecasting graph\\label{fig9}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(6)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("October",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# November  

<br><br>
```{r fig10,fig.cap = "Monthly forecasting graph\\label{fig10}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(7)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("November",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```
<br><br>

# December 

<br><br>

```{r fig11,fig.cap = "Monthly forecasting graph\\label{fig11}",echo=FALSE,message=FALSE, out.width='100%'}
monthdate<-ymd(params$report_month) %m+% months(8)
l_of_p<-make_prediction_monthly(monthdate)
monthreport_shaved<-ifelse(!is.na(l_of_p$peak_period),l_of_p$test-battery_size,l_of_p$test)

peak_period<-l_of_p$peak_period
low_peak_period<- l_of_p$low_peak_period
normal_period<-l_of_p$normal_period

E_peak<-l_of_p$ymax_list$test
E_price<-l_of_p$ymax_list$test/2
S_peak<-max(monthreport_shaved)
S_price<-max(monthreport_shaved)/2
Dif_price<-(l_of_p$ymax_list$test-max(monthreport_shaved))/2
Dif_peak<-l_of_p$ymax_list$test-max(monthreport_shaved)
temp<-data.frame("December",E_peak,S_peak,Dif_peak,E_price,S_price,Dif_price)
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
plot_ly(
    mode = 'lines+markers'
  ) %>%
  add_trace(
    y =  ~ l_of_p$test,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Test Data",
    line = list(color = ("black"))
  ) %>%
  add_trace(
    y =  ~ peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Discharging Period"),
    line = list(color = 'yellow')
  ) %>%
  add_trace(
    y =  ~ low_peak_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = paste("Charging Period"),
    line = list(color = 'blue')
  ) %>%
  add_trace(
    y =  ~ normal_period,
    x =  ~ l_of_p$hours,
    mode = 'lines',
    type = 'scatter',
    name = "Prediction",
    line = list(color = 'red')
  ) %>%
  add_trace(
    x =  ~ l_of_p$xcoord_list$test,
    y =  ~ l_of_p$ymax_list$test,
    mode = 'markers',
    type = 'scatter',
    name = paste("Highest Peak", l_of_p$ymax_list),
    marker = list(color = ("black"),size=13,symbol="triangle-up")
  )%>%
  layout(
    title = paste("From",strftime(as.POSIXct(l_of_p$hours[100]), format="%B %d, %Y"),
                  "to"
                  ,strftime(as.POSIXct(l_of_p$hours[length(l_of_p$hours)]), format="%B %d, %Y")),
    xaxis = list(
      title = 'Time',
      autotick = TRUE,
      showticklabels = TRUE
    ),
    yaxis = list(title = "Power Consumption")
  )
```



# Yearly Peak Shaving Results
The digital report of peak shaving activities is shown in Table (\@ref(tab:table1)) monthly. The table presents the comparison of Expected data and data after shaved. The data types have both power consumption and Price.
<br><br>
```{r table1,table.cap = "Yearly Results Table\\label{table1}",echo=FALSE, out.width='100%',fig.pos="H"}
temp<-data.frame("Total",sum(yearly_table$Expected_Peak),sum(yearly_table$Shaved_Peak)，sum(yearly_table$Peak_Reduction)，sum(yearly_table$Expected_Price),sum(yearly_table$Shaved_Price),sum(yearly_table$Price_Reduction))
colnames(temp)<-c('Month', "Expected_Peak","Shaved_Peak","Peak_Reduction","Expected_Price","Shaved_Price","Price_Reduction")
yearly_table<-rbind(yearly_table,temp)
knitr::kable(yearly_table,digits = 2,caption = "Yearly Results Table") %>% 
 # kbl(booktabs = TRUE) %>%
  kable_styling() %>%
  row_spec(13,bold=TRUE)

#knitr::kable(yearly_table,digits = 2,caption = "Yearly Results Table")
```